SoK: The Evolution of Defenses Against Web Application Attacks

### 2014-10-28 docs/questioning.tex
paragraph change
work on training subcategory

\begin{figure*}
\begin{center}
\leavevmode
\includegraphics[scale=0.55]{attacks-steps.pdf}
\end{center}
\caption{\label{fig:attacks}Attack model demonstrating web
application attacks based on executable source
code injection vulnerabilities. For every arrow there is a
corresponding tuple that includes the step number for
every attack. Note that {\sc xss} attacks can also involve
{\it phishing}. Every {\it locus} indicates a step where mechanisms
detect attacks. For every locus we provide the corresponding
references: ({\sc draft}).}
\end{figure*}

@@

In the case of {\sc xss} attacks that are based on JavaScript
or {\sc html}, consider a {\sc xor} function that encodes all source of a web
page on the server-side and then, on the client-side, the web browser decodes the
source by applying the same function again (locus {\sc x}).
Variations of this approach include:
{\it Noncespaces}~\cite{GC09} and {\it x{\sc js}}~\cite{APKLM10}
which randomize the instruction set of {\sc html} and
JavaScript respectively.

@@

In the case of Noncespaces, administrators must set
specific policies in a manner similar to a firewall
configuration language. This brings up questions
concerning the diagnostic performance of the mechanism
since the corresponding testing is insufficient
(see Table~\ref{tab:comp}).

@@

Training methods that detect JavaScript-driven {\sc xss} attacks
generate and store valid JavaScript code in various
forms, and detect attacks as outliers from the set of valid code statements.
{\it {\sc swap}}~\cite{WPLKK09} encodes all the legitimate scripts that exist in the
original application. Then, a JavaScript detection component placed in a web proxy
searches for injected scripts in the server's responses. If no injected scripts
are found, the proxy decodes the legitimate scripts and sends them to the
client.
% dimitro: more mechanisms TBA.

In the case of {\sc dsl}-driven injection attacks
the various countermeasures follow a similar pattern.
An early approach, {\it {\sc didafit}}~\cite{LLW02} detects
{\sc sql} injection attacks by recording all database transactions.
Subsequent refinements by Valeur et al.~\cite{VMV05}
tagged each transaction with the corresponding application
as an extension of their anomaly detection framework called
{\it libAnomaly}\footnote[6]{\url{http://seclab.cs.ucsb.edu/academic/projects/projects/libanomaly/}}.
Furthermore, {\sc amnesia}~\cite{HO05,HO06} is a tool that also detects {\sc sql}
injection attacks by associating a query model with the location of every
{\sc sql} statement within the application. Then at runtime,
monitors the application's execution to detect when {\sc sql} statements
diverge from the expected model.
{\it {\sc sd}river}~\cite{MS09,MKS09} is a signature-based
mechanism that prevents
{\sc sql} and {\sc xp}ath injection attacks against web applications. 
The signatures generated during a training phase,
are based on features that can depend either on the
code statement or on its execution environment (i.e. the stack trace).
Then, at runtime, the mechanism checks all statements for compliance
and can block code statements containing injected elements.
By associating a complete stack trace with the root of an {\sc sql} statement, 
the mechanism can correlate {\sc sql} statements with their call sites.  
This increases the specificity of the stored signatures and 
avoids false alarms. 
% dimitro: more mechanisms TBA.

>>>>

\begin{figure*}
\begin{center}
\leavevmode
\includegraphics[scale=0.57]{attacks-steps.pdf}
\end{center}
\caption{\label{fig:attacks}Attack model demonstrating web
application attacks based on executable source
code injection vulnerabilities. For every arrow there is a
corresponding tuple that includes the step number for
every attack. Note that {\sc xss} attacks can also involve
{\it phishing}. Every {\it locus} indicates a step where mechanisms
detect attacks. For every locus we provide the corresponding
references: ({\sc draft}).}
\end{figure*}

@@

In the case of {\sc xss} attacks that are based on JavaScript
or {\sc html}, consider a {\sc xor} function that encodes all source of a web
page on the server-side and then, on the client-side, the web browser decodes the
source by applying the same function again (locus {\sc x}).
Variations of this approach include:
{\it Noncespaces}~\cite{GC09} and {\it x{\sc js}}~\cite{APKLM10}
which randomize the instruction set of {\sc html} and
JavaScript respectively.
Contrary to x{\sc js}, in Noncespaces administrators must set
specific policies in a manner similar to a firewall
configuration language. This brings up questions
concerning the diagnostic performance of the mechanism
since the corresponding testing is insufficient
(see Table~\ref{tab:comp}).

@@

@@

Training methods that detect {\sc dsl}-driven injection attacks
generate and store valid code statements (i.e. {\sc sql}
or {\sc xp}ath queries) in various forms, and detect attacks
as outliers from the set of valid code statements.
An early approach, {\it {\sc didafit}}~\cite{LLW02} detects
{\sc sql} injection attacks by recording all database transactions.
Subsequent refinements by Valeur et al.~\cite{VMV05}
tagged each transaction with the corresponding application
as an extension of their anomaly detection framework called
{\it libAnomaly}. {\it {\sc sd}river}~\cite{MS09,MKS09} is
a signature-based mechanism that prevents {\sc sql} and
{\sc xp}ath injection attacks. The signatures generated
during a training phase, are based on features that can
depend either on the code statement or on its execution
environment (i.e. the stack trace).
Then, at runtime, the mechanism checks all statements for compliance
and can block code statements containing injected elements (locus {\sc z}).
% By associating a complete stack trace with the root of an {\sc sql} statement, 
% the mechanism can correlate {\sc sql} statements with their call sites.  
% This increases the specificity of the stored signatures and avoids false alarms.
Furthermore, {\sc amnesia}~\cite{HO05,HO06} is a tool that also detects {\sc sql}
injection attacks by associating a query model with the location of every
{\sc sql} statement within the application. Then at runtime,
monitors the application's execution to detect when {\sc sql} statements
diverge from the expected model.
% dimitro: more mechanisms TBA.

In the case of JavaScript-driven {\sc xss} attacks
the various countermeasures follow a similar pattern.
{\it {\sc swap}}~\cite{WPLKK09} follows a similar approach
with {\sc didafit} and creates a unique identifier
({\it script {\sc id}}) for every legitimate script on the server.
Then, a JavaScript detection component placed in a
web proxy (locus {\sc y}) searches for injected scripts
with no corresponding {\sc id} in the server's responses.
If no injected scripts are found, the proxy forwards the
request to the client.
% dimitro: more mechanisms TBA.
